


%%- http://webpages.iust.ac.ir/matashbar/teaching/schaum_probability.pdf

%%-- PAge 287
%%-- 9.9



People arrive at a telephone booth according to a Poisson process at an average rate of 12 per 
hour, and the average time for each call is an exponential r.v. with mean 2 minutes. 

\begin{enumerate}[(a)]
    \item  What is the probability that an arriving customer will find the telephone booth occupied? 
\item It is the policy of the telephone company to install additional booths if customers wait an 
average of 3 or more minutes for the phone. Find the average arrival rate needed to justify a 
second booth. 
\end{enumerate}

\section*{Solution}
\begin{itemize}
    \item (a) The telephone service can be modeled as an M/M/1 queueing system with $\lambda = 1/5$, $\mu = 1/2$ and $\rho = \lambda / \mu = 2/5$.
\item The probability that an arriving customer will find the telephone occupied is $P(L > 0)$, where 
$L$ is the average number of customers in the system. 
\item Thus, from Eq. (9.1 3), 
\end{itemize}
\[P(L>0) = 1-p_{0} = 1-(1-\rho) = \rho = \frac{2}{5} = 0.4 \]
\begin{itemize}
    \item (b) From Eq. (9.1 7), 
    \[ W_{q} = \frac{\lambda}{\mu(\mu-\lambda)} = \frac{\lambda}{0.5(0.5-\lambda)} \geq 3\]
from which we obtain $\lambda \geq 0.3$ per minute.
\item Thus, the required average arrival rate to justify the second 
booth is 18 per hour.
\end{itemize}

 

\end{document}
Let's address each part of the problem step by step.

### Part (a)

**Given:**
- Arrival rate, \( \lambda = 12 \) customers per hour
- Service time is an exponential random variable with mean 2 minutes

We need to convert the service rate to be consistent with the arrival rate:
- Service rate, \( \mu = \frac{1}{2} \) customers per minute, which is equivalent to \( \mu = 30 \) customers per hour

The traffic intensity \( \rho \) for an M/M/1 queueing system is:
\[ \rho = \frac{\lambda}{\mu} = \frac{12}{30} = 0.4 \]

The probability that an arriving customer will find the telephone booth occupied is \( P(L > 0) \), where \( L \) is the average number of customers in the system. This probability is:
\[ P(L > 0) = 1 - p_0 = 1 - (1 - \rho) = \rho = 0.4 \]

So, the probability that an arriving customer will find the telephone booth occupied is \( 0.4 \) or \( 40\% \).

### Part (b)

We need to find the average arrival rate needed to justify installing a second booth, given that customers wait an average of 3 or more minutes for the phone.

**Given:**
- The average waiting time \( W_q \) should not exceed 3 minutes.
- Current service rate \( \mu = 30 \) customers per hour.

The waiting time in the queue for an M/M/1 system is given by:
\[ W_q = \frac{\lambda}{\mu(\mu - \lambda)} \]

We want \( W_q \leq 3 \) minutes. Let's convert 3 minutes to hours:
\[ 3 \text{ minutes} = \frac{3}{60} \text{ hours} = 0.05 \text{ hours} \]

So:
\[ 0.05 \geq \frac{\lambda}{30(30 - \lambda)} \]

Solving for \( \lambda \):
\[ 0.05 \times 30(30 - \lambda) \geq \lambda \]
\[ 1.5(30 - \lambda) \geq \lambda \]
\[ 45 - 1.5\lambda \geq \lambda \]
\[ 45 \geq 2.5\lambda \]
\[ \lambda \leq \frac{45}{2.5} \]
\[ \lambda \leq 18 \text{ customers per hour} \]

Thus, the required average arrival rate to justify installing a second booth is 18 customers per hour or more.

Let me know if there's anything else you'd like to explore or clarify!